Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-10-25 causal-bandit/nips_2016/experiments.tex
updates experiment figuresq
updates figures to remove type3 fonts
updates sty file, experiment description adds github link

We compare Algorithms \ref{alg:simple} and \ref{alg:general} with Successive Elimination on the parallel bandit problem
under a variety of conditions, including where the importance weighted estimator used by Algorithm \ref{alg:general} is not truncated,
which is justified in this setting by Remark \ref{rem:truncate}. Throughout we use a model in which $Y$ depends only on a single variable $X_1$ (this is unknown to the algorithms). $Y_t \sim \bernoulli(\frac{1}{2}+\epsilon)$ if $X_1=1$ and $Y_t \sim \bernoulli(\frac{1}{2}-\epsilon')$ otherwise, where $\epsilon' = q_1\epsilon/(1-q_1)$. This leads to an expected reward of $\frac{1}{2}+\epsilon$ for $do(X_1=1)$, $\frac{1}{2}-\epsilon'$ for $do(X_1=0)$ and $\frac{1}{2}$ for all other actions. We set $\boldsymbol{q} = 0$ for $q_i \leq m$ and $\frac{1}{2}$ otherwise. Note that changing $m$ and thus $\boldsymbol{q}$ has no effect on the reward distribution.

%\eq{
%Y_t \sim \begin{cases}
%\bernoulli(\frac{1}{2}+\epsilon) & \text{if } X_1 = 1 \\
%\bernoulli(\frac{1}{2}-\frac{q_1}{1-q_1}\epsilon) & \text{otherwise}\,.
%\end{cases}
%}

We compare the performance of the Algorithm 1, which is specific to the parallel problem, but does not require knowledge of $\boldsymbol{q}$, with that of Algorithm 2 and the Successive Reject algorithm of \cite{audibert2010best}. For each experiment, we show the average regret over 10,000 simulations with error bars displaying three standard errors.

@@

\begin{figure}
    \begin{subfigure}[t]{0.3\textwidth}
		\centering    
    		\includegraphics[width=\textwidth]{exp_regret_vs_m_N50_T400_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
        \label{fig:simple_vs_m}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{experiment2_N50_a4_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
        \label{fig:simple_vs_T_vary_epsilon}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{experiment3_N50_s10000_20160519_1030.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
    		\label{fig:simple_vs_T}
    \end{subfigure}
    \caption{Experimental results}
    \label{fig:experiments}
\end{figure}

%\begin{figure}
%  \centering
%  \begin{minipage}[b]{0.3\textwidth}
%    \includegraphics[width=\textwidth]{exp_regret_vs_m_N50_T400_s10000_20160518_1534.pdf}
%    \caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
%    \label{fig:simple_vs_m}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.3\textwidth}
%    \includegraphics[width=\textwidth]{experiment2_N50_a4_s10000_20160518_1534.pdf}
%    \caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
%    \label{fig:simple_vs_T_vary_epsilon}
%  \end{minipage}
%  \hfill
%  \begin{minipage}[b]{0.3\textwidth}
%    \includegraphics[width=\textwidth]{experiment3_N50_s10000_20160518_1534.pdf}
%    \caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
%    \label{fig:simple_vs_T}
%  \end{minipage}
%\end{figure}

>>>>

We compare Algorithms \ref{alg:simple} and \ref{alg:general} with the Successive Reject algorithm of \cite{audibert2010best}, Thompson Sampling and UCB under a variety of conditions. Thomson sampling and UCB are optimized to minimize cumulative regret. We apply them in the fixed horizon, best arm identification setting by running them upto horizon $T$ and then selecting the arm with the highest empirical mean. The importance weighted estimator used by Algorithm \ref{alg:general} is not truncated, which is justified in this setting by Remark \ref{rem:truncate}.

Throughout we use a model in which $Y$ depends only on a single variable $X_1$ (this is unknown to the algorithms). $Y_t \sim \bernoulli(\frac{1}{2}+\epsilon)$ if $X_1=1$ and $Y_t \sim \bernoulli(\frac{1}{2}-\epsilon')$ otherwise, where $\epsilon' = q_1\epsilon/(1-q_1)$. This leads to an expected reward of $\frac{1}{2}+\epsilon$ for $do(X_1=1)$, $\frac{1}{2}-\epsilon'$ for $do(X_1=0)$ and $\frac{1}{2}$ for all other actions. We set $q_i = 0$ for $i \leq m$ and $\frac{1}{2}$ otherwise. Note that changing $m$ and thus $\boldsymbol{q}$ has no effect on the reward distribution. For each experiment, we show the average regret over 10,000 simulations with error bars displaying three standard errors. The code is available from \url{<https://github.com/finnhacks42/causal_bandits>}

@@

\begin{figure}
    \begin{subfigure}[t]{0.3\textwidth}
		\centering    
    		\includegraphics[width=\textwidth]{experiment1_20161020_1247.pdf}
    		\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
        \label{fig:simple_vs_m}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{experiment2_20161020_1249.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and $\epsilon = \sqrt{\frac{N}{8T}}$}
        \label{fig:simple_vs_T_vary_epsilon}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.3\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{experiment3_20161020_1252.pdf}
    		\caption{Simple regret vs horizon, $T$, with $N = 50$, $m=2$ and fixed $\epsilon = .3$}
    		\label{fig:simple_vs_T}
    \end{subfigure}
    \caption{Experimental results}
    \label{fig:experiments}
\end{figure}
